---
- title:"Map2" author:"Yu Du"
---

```{r setup, include=FALSE,warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo =FALSE,warning = FALSE,
               message = FALSE)
library(knitr)
library(dplyr)
library(tidyverse)
library(magrittr)
```


#Introduction:
#Read Data: The data is saved from the data cleaning process,rmd.
The Data is collected from the FEMA website.
```{r }
hurr<-read.csv("/Users/duyu/Desktop/MA615/hur.csv")
```

#Adding fips to the data.
```{r}
library(maps)
data(county.fips)
county.fips1 <- county.fips %>% separate(polyname, c("state", "county"), sep = ",")
#Make sure they all beginning with lower case.
county.fips1$state <- tolower(county.fips1$state)
county.fips1$county <- tolower(county.fips1$county)

hurr$state <- tolower(hurr$state)
hurr$county <- tolower(hurr$county)
# Add the fips into our funding data set
hurr <- left_join(hurr, county.fips1, by = c("county", "state"))
```

```{r}
county <- (map_data("county"))
county<-county%>%rename(state=region,county=subregion)
#county
state <- map_data("state")
```

#Calculating the sum of project Amount for each county in 2009-2020.
```{r}
hurrp<- hurr %>% 
  group_by(fips, state, county, year) %>% summarize(project = sum(projectAmount))

```


```{r}
hurrp <- right_join(hurrp, county, by = c("county", "state"))
head(hurrp,8)
```

#Using ggplot to draw a map for the total project amount of each state.
```{r}
hurrp<-na.omit(hurrp)
write.csv(hurrp,"hurrp.csv")
#max(hurrp$project)
#min(hurrp$project)
hurrp$project<-as.numeric(hurrp$project)
hurrp$Amount= cut(hurrp$project, breaks = c(0,2e+02,2e+04,2e+06,2e+08,2e+10),
                    include.lowest = TRUE)

plot1<-ggplot() + geom_polygon(data =hurrp, aes(long, lat, group = group,
                                                fill = Amount), 
                        color = "grey", size = 0.2, alpha = 1.6) + 
  geom_polygon(data = state, aes(long,lat, group = group),
                 color = "black", fill = "white", size = 0.2, alpha = 0.3) +
      scale_fill_brewer(palette = "Blues") +
  ggtitle("Project Amount in 2009-2020") +theme(plot.title = element_text(hjust = 0.5))
plot1
```

#Calculating the sum of federalShareObligated in 2009-2020.
```{r}
hurrd<- hurr %>% 
  group_by(fips, state, county, year) %>% summarize(federal = sum(federalShareObligated))
head(hurrd,8)
```


#Using ggplot to draw a map for the total federal share Obligrated of each state.
```{r}
hurrd <- right_join(hurrd, county, by = c("county", "state"))
hurrd<-na.omit(hurrd)
write.csv(hurrd,"hurrd.csv")
hurrd$federal<-as.numeric(hurrd$federal)
hurrd$Amount = cut(hurrd$federal, breaks = c(0,2e+03,2e+05,2e+07,2e+09,2e+10),
                    include.lowest = TRUE)

plot2<-ggplot() + geom_polygon(data =hurrd, aes(x = long, y = lat, group = group,
                                                fill = Amount), 
                        color = "grey", size = 0.2, alpha = 1.6) + 
  geom_polygon(data = state, aes(x = long, y = lat, group = group),
                 color = "black", fill = "white", size = 0.2, alpha = 0.3) +
      scale_fill_brewer(palette = "Blues") +
  ggtitle("Sum of Federal Share Obligated in 2009-2020") +theme(plot.title = element_text(hjust = 0.5))
plot2
```

#Using ggplotly
Now,I am trying to use ggplotly to show a clearer map for the previous dataframes.
```{r}
#This map is the same as the first map.
library(plotly)
library(dplyr)
state<-state
#county
#state
plot4<-ggplot(data =hurrp, aes(long, lat,group = group)) + geom_polygon(aes(
                                                fill = Amount), color = alpha("white",1/2), size = 0.05) + 
  geom_polygon(data = state,color = "grey", fill=NA) +
      scale_fill_brewer(palette = "Blues") +
  ggtitle("Total Project Amount from 2009 to 2020") +theme_void()
fig<-ggplotly(plot4)
fig

```


```{r}
#This map is improved from the second map.
state<-state
#county
#state
plot5<-ggplot(data =hurrd, aes(long, lat, group = group)) + geom_polygon(aes(
                                                fill = Amount), color = alpha("white",1/2), size = 0.05) + 
  geom_polygon(data = state,color = "grey", fill=NA) +
      scale_fill_brewer(palette = "Blues") +
  ggtitle("Total Federal Share Obligated 2009-2020") +theme_void()
fig<-ggplotly(plot5)
fig
```

```{r}
#citation("dplyr")
#citation("tidyverse")
#citation("magrittr")
#citation("maps")
#citation("plotly")
```

References

Hadley Wickham, Romain François, Lionel Henry and Kirill Müller (2020). dplyr: A Grammar of Data
Manipulation. R package version 1.0.2. https://CRAN.R-project.org/package=dplyr

Wickham et al., (2019). Welcome to the tidyverse. Journal of Open Source Software, 4(43), 1686,
https://doi.org/10.21105/joss.01686


Stefan Milton Bache and Hadley Wickham (2014). magrittr: A Forward-Pipe Operator for R. R package version
1.5. https://CRAN.R-project.org/package=magrittr

Original S code by Richard A. Becker, Allan R. Wilks. R version by Ray Brownrigg. Enhancements by Thomas P
Minka and Alex Deckmyn. (2018). maps: Draw Geographical Maps. R package version 3.3.0.
https://CRAN.R-project.org/package=maps

C. Sievert. Interactive Web-Based Data Visualization with R, plotly, and shiny. Chapman and Hall/CRC
Florida, 2020.

