---
title: "Presentation"
author: "Yu Du"
output: revealjs::revealjs_presentation
---

## Introduction

- The data is collected from the FEMA website
- The orginial Data contains 22 columns with over 700,000 rows
- very large dataset


## Important Columns for mapping

- Variables: year, state,county
- Outcomes: project Amount, federal share obligated
- project Amount:The estimated total cost of the Public Assistance grant project in dollars
- federal share obligated:The Public Assistance grant funding available to the grantee (State) in dollars


## Goal

- Calculate the total of two outcomes (project Amount, federal share obligated) in each county from 2009 to 2020
- Look at if there is any trend
- Compare two maps

## Data Cleaning Steps

step one 
- choose the 'Hurricane' as the incident of type
- the incident type will affect the types of assistance available 


step two
- choose the year from 2009 to 2020




## Plot the total project Amount from 2009 to 2020

```{r,echo=FALSE,message=FALSE}
library(ggplot2)
library(plotly)
library(maps)
state<-map_data("state")
hurr1<-read.csv("/Users/duyu/Desktop/MA615/Mapping/Mapping/hurrp.csv")
hurr1<-hurr1[,2:9]
 hurr1$project<-as.numeric(hurr1$project)
  hurr1$Amount=cut(hurr1$project, breaks = c(0,2e+02,2e+04,2e+06,2e+08,2e+10),
                    include.lowest = TRUE)
    ggplot1<-ggplot() + geom_polygon(data =hurr1, aes(long, lat, group = group,
                                                    fill = Amount), 
                                   color = "grey", size = 0.2, alpha = 1.6) + 
      geom_polygon(data = state, aes(long,lat, group = group),
                   color = "black", fill = "white", size = 0.2, alpha = 0.3) +
      scale_fill_brewer(palette = "Blues") +
      ggtitle("Total Project Amount in 2009-2020") +theme(plot.title = element_text(hjust = 0.5))
    ggplot1
```


## Plot the total federal share obligated from 2009 to 2020.

```{r, echo=FALSE}
hurr2<-read.csv("/Users/duyu/Desktop/MA615/Mapping/Mapping/hurrd.csv")
hurr2<-hurr2[,2:9]
 hurr2$federal<-as.numeric(hurr2$federal)
    hurr2$Amount = cut(hurr2$federal, breaks = c(0,2e+02,2e+04,2e+06,2e+08,2e+10),
                       include.lowest = TRUE)
    
    ggplot2<-ggplot() + geom_polygon(data =hurr2, aes(x = long, y = lat, group = group,
                                                    fill = Amount), 
                                   color = "grey", size = 0.2, alpha = 1.6) + 
      geom_polygon(data = state, aes(x = long, y = lat, group = group),
                   color = "black", fill = "white", size = 0.2, alpha = 0.3) +
      scale_fill_brewer(palette = "Blues") +
      ggtitle("Total Federal Share Obligated in 2009-2020") +theme(plot.title = element_text(hjust = 0.5))
    ggplot2
```

## ShinyApp
contains ggplotly maps: https://ydu199.shinyapps.io/Mapping/

## Results/Observations
- The southeast US suffers the incident 'Hurricane'.
- Coastal counties tend to have higher project amount and federal share obligated from 2009 to 2020.
- In some counties, total project amount is higher than total federal share obligated from 2009 to 2020.

## What can improve or add
- can set time intervals in 2009-2020 to look at the data more specifically.
- can look at other incidents to find if some might have the similar result.

## Thanks